%-------------------------
% Viraj Sanghavi — Resume (One Page)
% Paste into Overleaf, compile with pdflatex
%-------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%--- Custom commands ---

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%==============================================
\begin{document}
%==============================================

%--- HEADER ---
\begin{center}
    \textbf{\Huge \scshape Viraj Sanghavi} \\ \vspace{4pt}
    \small 8104488190 $|$
    \href{mailto:virajsanghavi000@gmail.com}{\underline{virajsanghavi000@gmail.com}} $|$
    \href{https://linkedin.com/in/virajsanghavi}{\underline{LinkedIn}} $|$
    \href{https://github.com/VirajSanghavi007}{\underline{GitHub}} $|$
    \href{https://kaggle.com/virajsanghavi}{\underline{Kaggle}}
\end{center}

%--- EDUCATION ---
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Dwarkadas J. Sanghvi College of Engineering}{Mumbai, India}
    {B.Tech in Computer Engineering \textnormal{--- CGPA: \textbf{9.18}}}{2024 -- 2028}
\resumeSubHeadingListEnd

%--- EXPERIENCE ---
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Developer Intern}{Jun 2026 -- Aug 2026}
    {ITAakash Strategic Software Pvt. Ltd.}{Mumbai, India}
    \resumeItemListStart
      \resumeItem{Update with responsibilities and deliverables once internship begins.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--- PROJECTS ---
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{\href{https://github.com/VirajSanghavi007}{AlgoTrade-X}} $|$
     \emph{Python, Pandas, NumPy, Scikit-learn, Backtrader}}{2025}
    \resumeItemListStart
      \resumeItem{Built an end-to-end quantitative trading research system backtesting momentum, mean-reversion, and ML-driven signal strategies on equity and derivatives data.}
      \resumeItem{Evaluated strategies using Sharpe ratio, max drawdown, and risk-adjusted return metrics across multiple market regimes.}
      \resumeItem{Designed modular pipeline separating data ingestion, feature engineering, signal generation, and execution layers for reproducible research.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{\href{https://github.com/VirajSanghavi007/ADAPT-Synthetix}{ADAPT-Synthetix}} $|$
     \emph{Python, Wav2Vec2, FastAPI, PostgreSQL, Docker, React}}{2025}
    \resumeItemListStart
      \resumeItem{Built research-grade adaptive ASR pipeline: Wav2Vec2 transcription, 8-feature acoustic noise fingerprinting across 5 environment categories, and TTS-driven closed-loop remediation.}
      \resumeItem{Implemented phoneme-level drift monitor with 20-utterance rolling window triggering LoRA fine-tuning data prep when 5+ phonemes enter high-risk state.}
      \resumeItem{Deployed full-stack system (FastAPI, React, PostgreSQL, Docker) with CI/CD via GitHub Actions on Render.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{\href{https://github.com/VirajSanghavi007/IdeaHackathon}{AML Intelligence Platform}} $|$
     \emph{Python, FastAPI, NetworkX, Scikit-learn, Cytoscape.js}}{2025}
    \resumeItemListStart
      \resumeItem{\textit{iDEA 2.0 Hackathon --- Union Bank of India PS3: Fund Flow Tracking for Fraud Detection --- Team Zeta}}
      \resumeItem{Built graph-native AML system detecting 8 structural typologies (Cycle, Fan-Out, Fan-In, Scatter-Gather, Bipartite, Stack) plus 7 behavioural signals (structuring, smurfing, layering) on 500k IBM synthetic transactions.}
      \resumeItem{Random Forest classifier (200 trees, 16 graph features): \textbf{F1 0.67, Precision 0.83}; deployed investigation dashboard live on Render.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{\href{https://github.com/VirajSanghavi007}{Swipe to Export}} $|$
     \emph{Python, Scikit-learn}}{2024}
    \resumeItemListStart
      \resumeItem{\textit{LOC Hackathon} --- ML model matching exporters to importers using PCA dimensionality reduction and Bayesian probabilistic confidence scoring on real trade datasets.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%--- RESEARCH ---
\section{Research \& Extracurriculars}
\resumeSubHeadingListStart
  \resumeSubheading
    {DJS Anveshan --- Research Club}{2024 -- Present}
    {Publicity \& Research Member}{Dwarkadas J. Sanghvi College of Engineering}
    \resumeItemListStart
      \resumeItem{Authored problem discovery report on a critical Federated Learning failure mode: robust aggregation filters silently discarding valid non-IID updates from minority institutions in cross-institutional fraud detection.}
      \resumeItem{Identified unaddressed gap in FL security literature as of 2025, citing IEEE Transactions on Big Data and JPMorgan's Project Aikya.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%--- SKILLS ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, JavaScript, SQL} \\
    \textbf{ML / Data}{: Scikit-learn, NumPy, Pandas, Wav2Vec2, LoRA, NetworkX, Matplotlib} \\
    \textbf{Eng / Infra}{: FastAPI, React, Docker, PostgreSQL, Git, GitHub Actions, Backtrader} \\
    \textbf{Domains}{: Algorithmic Trading, ASR Systems, Graph-Based Fraud Detection, Supply Chain Analytics}
  }}
\end{itemize}

%--- CERTIFICATIONS ---
\section{Certifications}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Intro to Machine Learning} $|$ \emph{Kaggle Learn}}{2025}
\resumeSubHeadingListEnd

%==============================================
\end{document}
